---
title: "Filtering Non-informative Lipids"
author: "Meeyoung Park"
date: "April 5, 2016"
output: html_document
---

```{r setup, include=FALSE}
    library(ggplot2)
```

### Data Cleaning
0. The normalized data from the Core are used to calculate CV. (manually done in excel)
* CV = STDEV/AVERAGE * 100)
* Column names: Name/CV/DataforSamples
* Check if all sample column order and names are same! 
* Output filename: "_Pos.txt", "_Neg.txt"

1. Separate Name column to Lipid/Adduct/RT ("1_separated_lipid_name.pl")
* Input filename: "_Pos.txt", "_Neg.txt"
* Column names: Lipid/Adduct/RT/CV/DataforSamples
* Output filename: "_LipidSeparated.txt"

2. Remove redundant species - select the lesser CV ("2_RemoveDuplicateLipids.R")
* Output filename: "_nonRedundant.txt"

3. Separated Lipid column to Class/Carbon/Saturation ("3_extract_lipid_class.pl")
* Input filename: "_nonRedundant.txt"
* Column names: "Class/Carbon/Saturation/CV/DataforSamples
* Output filename: "_LipidClass.txt"

4. Remove odd chain species ("4_RemoveOddChain.R")
* Input filename: "_LipidClass.txt"
* Check even number in saturation column for animals
* Output filename: "*_noOdd.txt"

5. Remove unrelated class in each polar group and combine them ("5_ExtractRelavantClass.R")
* Refer to the positive/negative list of lipid class
* Input filename: "*_noOdd.txt"
* Output filename: "*_final.txt"

7. 
```{r echo = FALSE}
        SCN = read.delim("./StatisticalAnalysis/SCN_final.txt", header = TRUE, sep = "\t")
    Plasma = read.delim("./StatisticalAnalysis/Plasma_final.txt", header = TRUE, sep = "\t")
    Liver = read.delim("./StatisticalAnalysis/Liver_final.txt", header = TRUE, sep = "\t")
```
### Final processed lipid data summary

SCN:
```{r echo = FALSE}
dim(SCN)
```
Plasma:
```{r  echo = FALSE}
dim(Plasma)
```
Liver:
```{r  echo = FALSE}
dim(Liver)
```

Done!