---
title: "Lipidomics Analysis on High fat diet mice model"
author: "Meeyoung Park"
date: "March 24, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Aims/hypothesis Patients with impaired glucose tolerance (IGT) are prone to developing peripheral neuropathy (PN), a common complication observed in diabetic patients. To investigate the mechanisms of PN in IGT, appropriate animal models are required. Using mice of various strains/backgrounds, our aim was to identify a model that developed an early and robust neuropathy when placed on a high-fat diet (HFD).

Methods: Neuropathy development in six mouse strains/genotypes (BKS-wt, BKS-db/+, BL6-wt, BL6-db/+, BTBR-wt, BTBR-ob/+) fed a 54% HFD was investigated. Lipidomics data from nerve, liver, and plasma for each mouse strain were analyzed.

Results: All HFD-fed mice developed PN; however, a more robust neuropathic phenotype consisting of large fiber dysfunction and small fiber degeneration occurred consistently in HFD-fed BL6-wt mice.   

Conclusions/interpretation: We conclude that HFD-fed BL6-wt mice are a favorable model for investigating PN during a state of IGT.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
